% This file contains the content for a main section
\regularsectionformat
%% Modify below this line %%
\chapter{Document Types}

ACES technical documentation is a collection of Society of Motion Picture and Television Engineers (SMPTE) Engineering Documents, Academy Specifications, Academy Procedures and Academy Technical Bulletins. These document types are described below.

\section{SMPTE Engineering Documents}
Certain ACES technical specifications have been standardized by SMPTE, the industry's accredited standards development organization. For more information on SMPTE standards, please visit http://www.smpte.org.

\section{Academy Specification}
An Academy Specification is a document that states basic technical specifications, dimensions or criteria that describe the form and function of a system and/or its components.  Specifications may include informative text describing basic usage of the specification and other contextual information. Academy Specification numbers use the following format: S-xxxx-yyy where xxxx is the publication year and yyy is the document sequence number (a maximum of 999 Academy Specifications may be published in any year).

\section{Academy Procedure}
An Academy Procedure is a document that provides a set of recommended step-by-step instructions intended to facilitate the implementation of one or more specifications. Academy Procedure numbers use the following format: P-xxxx-yyy where xxxx is the publication year and yyy is the document sequence number (a maximum of 999 Academy Procedures may be published in any year).

\section{Academy Technical Bulletin}
An Academy Technical Bulletin is a document, often tutorial in nature, intended to provide a broad system overview, in-depth usage information, in-depth specification derivation not required to implement a specification, or any other technical information or reporting that falls outside the scope of an Academy Specification or Procedure. Academy Technical Bulletin numbers use the following format: TB-xxxx-yyy where xxxx is the publication year and yyy is the document sequence number (a maximum of 999 Academy Technical Bulletins may be published in any year).
