\newpage
\section{ACES Leadership}
As noted earlier, ACES continues to be a project organized under the auspices of the Academy Science and Technology Council, although the Council's long-term goal is to transfer project leadership to an appropriate, industry-led leadership structure such as the Academy Software Foundation. As such, a Council project oversight committee is still required, which takes the form of ``ACES Leadership.'' 

ACES Leadership is the team tasked with accountability to the Council for ACES adoption and ongoing development activities. ACES Leadership also sets the broad strategic goals of the ACES project; driven by the needs of the industry for digital image interchange, color management and long-term archiving. ACES Leadership works with the Architecture and Implementation TACs to develop these goals and to focus Working Group activities on achieving these goals. Along with accountability for the ACES project, ACES Leadership is responsible for reviewing and ratifying approved TAC recommendations.

As ACES branding makes use of the Academy trademarks, ACES Leadership organizes and oversees ACES marketing, Logo Program and public communications activities. ACES Leadership makes use of the Academy staff's ability to handle private discussions with ACES adopters and to provide ``firewalling'' of sensitive information.



\subsection{Membership}
The membership of ACES Leadership shall consist of the following:
\begin{itemize}
    \item A volunteer ACES Project Chair selected from the Science and Technology Council membership
    \item Two (2) volunteer ACES Project Vice-Chairs
    \item Selected Science and Technology Council staff and consultants (as needed)
\end{itemize}

\subsection{Scope and Responsibilities}
The scope and responsibilities of ACES leadership shall include:
\begin{itemize}
    \item ACES project strategy definition and execution
    \item Work item definition, prioritization and approval
    \item All public communications regarding the ACES project
    \item ACES project marketing efforts
    \item ACESCentral.com administration
    \item Other leadership and management functions as required
\end{itemize}

\subsection{Meetings}
The ACES Leadership team meets weekly to track ACES project progress, plan for public events and discuss specific issues as needed. Regular “state of the project” reports will be posted to ACESCentral.com by the ACES Project chair and vice-chairs.
