\newpage
\section{ACES Implementation Technical Advisory Council}
The ACES Implementation Technical Advisory Council (Implementation TAC) is responsible for the peer review and acceptance of Working Group deliverables that impact real-world implementations or are impacted by real-world implementation considerations. The Implementation TAC ensures Working Group deliverables are consistent with ACES implementation strategy and goals. The Implementation TAC is also responsible for ensuring Working Group activities are within their approved scope and that timelines are met. The Implementation TAC does not engineer solutions to particular problems but serves as a body to provide guidance and expert advice to the Working Groups it oversees. Implementation TAC membership is by invitation of the TAC chair consistent with the parameters described below. Implementation TAC recommendations requiring a vote are approved by a simple majority of voting members. TAC members may not always agree on specific decisions but should seek to reach consensus that is in the best interest the ACES community.  TAC recommendations are forwarded to ACES Leadership for ratification.  Membership on the TAC is for 1 year, renewable for up to 2 additional years.

\subsection{Leadership and Voting Members}
The Implementation TAC should have between 12--18 members.  The voting membership of the Implementation TAC should be composed as follows:

\begin{itemize}
    \item The ACES Implementation TAC Chair who is one of the ACES Project Vice Chairs
    \item ACES Product Partner representatives, with no more that one from each ACES Logo Program product category, comprising approximately 30--40\% of the TAC
    \item Post-production facility representatives comprising approximately 10--20\% of the TAC
    \item Visual effects facility/animation studio representatives comprising approximately 10--20\% of the TAC
    \item Game development company representatives comprising approximately 10--20\% of the TAC
    \item One (1) representative from the OpenColorIO project
\end{itemize}

\subsection{Scope and Responsibilities}
The scope and responsibilities of the ACES Implementation TAC shall include:

\begin{itemize}
    \item The ACES Reference implementation
    \item ACES developer and end-user tools (e.g. e.g. rawtoaces, ACES container reference implementation, etc.)
    \item Advice on Logo Program requirements
    \item End-user documentation
    \item ACES plug-fests
    \item Other ACES implementation related-topics as needed and agreed to by ACES Leadership
\end{itemize}

\subsection{Meetings}
Meetings of the Implementation TAC will occur quarterly and will be open to the public. Meeting notifications will be posted to ACEScentral.com in advance. Non-voting meeting attendees may participate in the meeting discussions and provide relevant commentary at the discretion of the Implementation TAC Chair. Efforts will be made to record the meetings for later review. 