\newpage
\section{Working Groups}
Working Groups are intended to be short lived, issue based, pop-up groups driven by the ACES community's need to address issues and develop features for future versions of ACES. Working Groups serve as the mechanism for engineering, software development, documentation production, and other detailed development tasks for ACES. A Working Group may be proposed by any member of the ACES community willing and able to lead the activity by completing the Working Group Proposal form included in Appendix A and forwarding it to ACES Leadership, although socialization of proposal ideas within ACES Central and the appropriate Advisory Council is strongly recommended. Advisory Councils and ACES Leadership will work with the proposal submitter to refine the proposal, and will approve the proposal if all conditions for new projects are met. Advisory Councils and ACES Leadership may also initiate the Working Group proposal process if the need is clear and the environment is amenable to doing the work.

Working Group membership is open to anyone willing and able to actively and productively contribute to the work product. Working Group activity is visible to the public and open discussion within the Working Group's ACES Central discussion thread.

The Working Group chair presents interim status reports and final deliverables to the parent Advisory Council for review. When complete, the Working Group deliverables are forwarded by the parent Advisory Council to ACES Leadership for final review and release approval.

Working Group meetings will occur regularly, be advertised on ACEScentral.com in advance, and be open to the public. Effort will be made to record the meetings for later review and documentation purposes.
The complete process from Working Group proposal to release of the Working Group deliverable(s) is outlined in the flowchart in Appendix B.