% This section contains the content for the Terms and Definitions
\numberedformat
\chapter{Terms and Definitions}
The following terms and definitions are used in this document.
%% Modify below this line %%

\term{ACESclip}
Collection of image files color-managed using the Academy Color Encoding System (ACES).

\term{ACESclip file, ACES Clip-level Metadata File}
Metadata “sidecar” XML-based file that contains information describing an ACESclip.

\term{ACES Encodings}
Color encoding specifications specified as part of the Academy Color Encoding System, e.g., ACES2065-1, ACEScc, etc.

\term{ACES File Formats}
Digital data containers specified as part of the Academy Color Encoding System, e.g., ACESclip files, ACES Image Container (SMPTE ST2065-4), etc.

\term{ACES Product Partners}
Companies that integrate ACES concepts and components into their products and/or services.

\term{ACES System}
Complete set of components that comprise the Academy Color Encoding System.

\term{ACES System Release}
Published ACES System.

\term{ACES Transforms}
Color transformations specified as part of the Academy Color Encoding System, e.g., Reference Rendering Transform (RRT), Output Device Transforms (ODT), etc.

\term{CTL files}
Files containing Color Transformation Language code. CTL files are the primary documentation for ACES transforms.

\term{Implementation Transforms}
ACES System transforms implemented by ACES Product Partners, likely as a Color Look-up Table or as GPU or CPU code.

\term{Transform Identifiers}
Tags that identify specific ACES Transforms.